Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
writting up Conclusion.

\begin{itemize}
\item
    We discussed how to apply BDD to Haskell.
\item
    We proposed to use Doctest for user documentation and Hspec for
    code documentation.
\item
    We added markup support for properties and examples to Haddock.
    And we implemented Doctest, to verify examples and test properties
    from Haddock comments.
\item
    We extend Hspec with a set of combinators for expectations.
\item
    With these two tools, specification can also be used for
    documentation and automatic testing.
\item
    We describe a mechanism, that can automatically discover all specs
    of a project.
\item
    We think that this enhances the value of test code, and we hope
    that it will motivate Haskell programmers to write more and better
    tests.
\end{itemize}

>>>>

This paper discussed how to apply behavior driven development to
Haskell.  We proposed to use Doctest for user documentation and Hspec
for code documentation.  For user documentation, two markups for
properties and examples are added to Haddock.  And we implemented
Doctest to verify examples and test properties from Haddock comments.
For code documentation, a set of combinators for expectations is
extended for Hspec.  With these two tools, specification can also be
used for documentation and automatic testing.  We also described a
mechanism that can automatically discover all specs of a project.  We
think that our approach enhances the value of test code, and we hope
that three-in-one aspect will motivate Haskell programmers to write
more and better
